Genetic Dilution erodes productivity: Exploring farmers' low adoption levels of improved maize in Ethiopia

### 2022-11-04 paper.tex

Since ESS1-ESS3 do not have DNA fingerprinting, we are left with only self-reports of hybrid use. We use these variables in a Group Random Coefficiens (GRC) approach to investigate the heterogeneous effects of adoption. The advantage of the GRC approach is that we do not rely on identification from a valid instrument, but on modelling the heterogeneity directly through a projection of adoption returns on their observed ``trajectory'' of adoption. This allows us to directly capture two effects: heterogeneous effects in the form of so-called ``comparative advantage" of adoption, and, under the assumption of linearity in comparative advantage, a description of the overall economy's sorting of farmers based on their comparative advantage. The first is important because it is able to disentangle the effect of a general household's agricultural ability (which can be thought of as a fixed effect) and their adoption-specific potential. The second parameter can tell us whether the economy sort farmers in a way that is commensurate with providing those that would benefit the most from adoption actually adopting, or whether there are barriers interfering with that. See \cite{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} for more information on the assumptions involved for the GRC approach.

>>>>

Since ESS1-ESS3 do not have DNA fingerprinting, we are left with only self-reports of hybrid use. We use these variables in a Group Random Coefficients (GRC) approach to investigate the heterogeneous effects of adoption. The advantage of the GRC approach is that we do not rely on identification from a valid instrument, but on modeling the heterogeneity directly through a projection of adoption returns on their observed ``trajectory'' of adoption. This allows us to directly capture two effects: heterogeneous effects in the form of the so-called ``comparative advantage" of adoption, and, under the assumption of linearity in comparative advantage, a description of the overall economy's sorting of farmers based on their comparative advantage. The first is important because it is able to disentangle the effect of a general household's agricultural ability (which can be thought of as a fixed effect) and their adoption-specific potential. The second parameter can tell us whether the economy sort farmers in a way that is commensurate with providing those that would benefit the most from adoption actually adopting, or whether there are barriers interfering with that. See \cite{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} for more information on the assumptions involved for the GRC approach.
